### 2023-06-29 paper/main.tex
..

The shifted spatially filtered driving function reads as
\begin{multline}
    d'_x(s,t+ \tau(s) ) = \int h_x(s-s_0) \, d(s_0,t+ \tau(s) ) \, \td s_0 = \\
    \int h_x(s-s_0) \, A^D(s_0)\, \delta(s_0,t+ \left(\tau(s)-\tau(s_0)\right)  ) \, \td s_0.
    \label{eq:spat_conv2}
\end{multline}
In order to evaluate the spatial convolution the generalized sifting property of the Dirac-delta may be applied \cite{Firtha2019phd}, which states that
\begin{equation}
    \int f(s_0) \delta(g(s_0)) \td s_0 = \sum_i \frac{f(s_i)}{| \frac{\partial}{\partial s_0} g(s_0) |_{s = s_i}}, \hspace{3mm} g(s_i) = 0.
\end{equation}
In the present problem the zeros of the Dirac's argument are found where
\begin{equation}
    \tau(s_i) = t + \tau(s)
    \label{eq:zero}
\end{equation}
is satisfied.
In the following it is assumed that a single zero $s_i$ exists, satisfying \eqref{eq:zero}.
This assumption means that the wavefront arrives at each SSD element at a unique time instant, being strictly true for a virtual plane wave and a linear SSD.
The derivative of the phase function is given by
\begin{equation}
    \frac{\partial}{\partial s_0} g(s_0) = - \frac{\partial}{\partial s_0} \tau(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
\end{equation}
i.e. it is the tangential component of the local propagation vector.
With the above assumptions the integral \eqref{eq:spat_conv2} can be evaluated, yielding
\begin{equation}
    d'_x(s,t+ \tau(s) ) =  \frac{ c }{|\hat{k}_t^P(s_i)|} \, h_x(s-s_i) \, A^D(s_i)
    .
    \label{eq:spat_conv_eval}
\end{equation}

@@

The present contribution discussed a novel local Wave Field Synthesis approach, relying on a suitable filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals, with the bandlimit depending on the virtual source model.

>>>>

The shifted spatially filtered driving function reads as
\begin{multline}
    d'_x(s,t+ \tau(s) ) = \int h_x(s-s_0) \, d(s_0,t+ \tau(s) ) \, \td s_0 = \\
    \int h_x(s-s_0) \, A^D(s_0)\, \delta(s_0,t+ \left(\tau(s)-\tau(s_0)\right)  ) \, \td s_0.
    \label{eq:spat_conv2}
\end{multline}
In order to evaluate the spatial convolution the generalized sifting property of the Dirac-delta may be applied \cite{Firtha2019phd, Jackson1999}, which states that
\begin{equation}
    \int f(s_0) \delta(g(s_0)) \td s_0 = \sum_i \frac{f(s_i)}{| \frac{\partial}{\partial s_0} g(s_0) |_{s = s_i}}, \hspace{3mm} g(s_i) = 0.
\end{equation}
In the present problem the zeros of the Dirac's argument are found where
\begin{equation}
    \tau(s_i) = t + \tau(s)
    \label{eq:zero}
\end{equation}
is satisfied.
In the following it is assumed that a single zero $s_i$ exists, satisfying \eqref{eq:zero}.
This assumption means that the wavefront arrives at each SSD element at a unique time instant, being strictly true for a virtual plane wave and a linear SSD.
The derivative of the phase function is given by
\begin{equation}
    \frac{\partial}{\partial s_0} g(s_0) = - \frac{\partial}{\partial s_0} \tau(s_0) = -\frac{\hat{k}_t^P(s_0)}{c},
\end{equation}
i.e. it is the tangential component of the local propagation vector.
With the above assumptions the integral \eqref{eq:spat_conv2} can be evaluated, yielding
\begin{equation}
    d'_x(s,t+ \tau(s) ) =  \frac{ c }{|\hat{k}_t^P(s_i)|} \, h_x(s-s_i) \, A^D(s_i)
    .
    \label{eq:spat_conv_eval}
\end{equation}

@@

The present contribution discussed a novel local Wave Field Synthesis approach, relying on a suitable filter transformation that allows derivation of a temporal filter bank from an arbitrary spatial filter.
By transforming spatial antialiasing filters to a temporal filter bank, antialiasing can be performed by simple temporal bandlimitation of the SSD driving signals.
With the above antialiasing strategy local WFS can be implemented by choosing an appropriate spatial antialiasing filter based on a predefined reference listening position.
